---
title: "BL_Revision"
author: "JM Schneider"
date: "4/14/2020"
output: html_document
---

## Library Import
```{r,include=FALSE,echo=FALSE,warning=FALSE}
#Loading library
library(ez); library(ggplot2); library(multcomp); library(nlme); library(pastecs); library(reshape)
library(Hmisc); library (WRS2); library(lme4); library(lmerTest); library(plyr); library(splitstackshape) 
library(naniar); library(tidyr); library(dplyr); library(memisc); library(psychReport); library(foreign); library(interactions); library(corrplot)
```
## Flatten MAtrix Function
```{r,include=FALSE,echo=FALSE,warning=FALSE}
# ++++++++++++++++++++++++++++
# flattenCorrMatrix
# ++++++++++++++++++++++++++++
# cormat : matrix of the correlation coefficients
# pmat : matrix of the correlation p-values
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
  )
}
```
## Additional Preset and Working Directory
```{r}
rm(list=ls())

# Max print output.
options(max.print=1e9)
options(dplyr.print_max = 1e10)

setwd("/Users/julieschneider/Julie_Personal/Projects/WLdevdiff/R_Data/")
df_ast=read.csv('BL_Ast.csv')
df_MP=read.csv('BL_MP.csv')
df_extract=read.csv('Data_extract_042720.csv')
df_age=read.csv('BL_Revisions.csv')
```

## Combine dataframes
```{r}
df_ast_subset <- df_ast[c(1:15)]
df_ast_subset <-rename(df_ast_subset, c("Subject.Code"="Participant"))

df_age_subset <- df_age[c(1:4)]

#merge two dataframes based on subject ID
df_partial <- merge(df_MP,df_extract,by="Participant")
df_partial_2 <- merge(df_partial,df_age,by="Participant")
df_overall <- merge(df_partial_2,df_ast_subset,by="Participant")
write.csv(df_overall , "BL_Revision_New_Extract.csv")
```

## Make Factors into Numeric Values
```{r}
df_overall$Theta<-as.numeric(df_overall$Theta)
df_overall$Beta<-as.numeric(df_overall$Beta)
df_overall$Alpha<-as.numeric(df_overall$Alpha)
df_overall$Gamma<-as.numeric(df_overall$Gamma)
df_overall$age<-as.numeric(df_overall$age)
df_overall$Participant<-as.numeric(df_overall$Participant)
df_overall$PPVT.Raw.Score<-as.numeric(df_overall$PPVT.Raw.Score)
df_overall$GortCo<-as.numeric(df_overall$GortCo)
df_overall$DigSpa<-as.numeric(df_overall$DigSpa)
df_overall$MP_PC<-as.numeric(df_overall$MP_PC)
df_overall$PPVT<-as.numeric(df_overall$PPVT)
df_overall$MatEd5<-as.numeric(df_overall$MatEd5)

```

## Establish Groups
```{r}
children <- df_overall[which(df_overall$AgeGroup == 1),]
adolescents <- df_overall[which(df_overall$AgeGroup == 2),]
```

## Correlations within each group
```{r}
myvars <- c("MP_PC","Alpha","Theta","Beta","PPVT","GortCo","DigSpa")
child_corr_subset <- children[myvars]
adol_corr_subset <- adolescents[myvars]
child_res <-cor(child_corr_subset)
child_res2<-rcorr(as.matrix(child_corr_subset))
#flattenCorrMatrix(child_res2$r, child_res2$P)
corrplot(child_res2$r, type="upper", order="hclust", 
         p.mat = child_res2$P, sig.level = 0.05, insig = "blank")
```
## Overall LMEM no cogntive variables
```{r}
child.model <- glm(MP_PC ~ 1 + Theta + Beta + Alpha, data = children)
adol.model <- glm(MP_PC ~ 1 + Theta + Beta + Alpha + Gamma, data = adolescents)
overall.model <- glm(MP_PC ~ 1 + Theta + Beta + Alpha + Gamma + age, data = df_overall)

summary(child.model)
summary(adol.model)
summary(overall.model)
```

## Theta
```{r}
child.theta.model <- glm(MP_PC ~ 1 + Theta*GortCo + Theta*PPVT + Theta*DigSpa + Beta + Alpha + age, data = children)
adol.theta.model <- glm(MP_PC ~ 1 + Theta*GortCo + Theta*PPVT + Theta*DigSpa + Beta + Alpha + Gamma + age, data = adolescents)

summary(child.theta.model)
summary(adol.theta.model)
```

## Alpha
```{r}
child.alpha.model <- glm(MP_PC ~ 1 + Alpha*GortCo + Alpha*PPVT + Alpha*DigSpa + Theta + Beta + age, data = children)
adol.alpha.model <- glm(MP_PC ~ 1 + Alpha*GortCo + Alpha*PPVT + Alpha*DigSpa + Theta + Beta + Gamma + age, data = adolescents)

summary(child.alpha.model)
summary(adol.alpha.model)
```
## Beta
```{r}
child.beta.model <- glm(MP_PC ~ 1 + Beta*GortCo + Beta*PPVT + Beta*DigSpa + Theta + Alpha + age, data = children)
adol.beta.model <- glm(MP_PC ~ 1 + Beta*GortCo + Beta*PPVT + Beta*DigSpa + Theta + Alpha + Gamma + age, data = adolescents)

summary(child.beta.model)
summary(adol.beta.model)
```

## Gamma
```{r}
adol.gamma.model <- glm(MP_PC ~ 1 + Gamma*GortCo + Gamma*PPVT + Gamma*DigSpa + Theta + Alpha + Beta + age, data = adolescents)

summary(adol.gamma.model)
```
## Reading and Word Learning
```{r}
alpha.model <- lmer(MP_PC ~ 1 + Alpha*GortCo*age + (1|age), data = children)
beta.model <- lmer(MP_PC ~ 1 + Beta*GortCo*age + (1|age), data = children)
theta.model <- lmer(MP_PC ~ 1 + Theta*GortCo*age + (1|age), data = children)

AIC(alpha.model,beta.model,theta.model)

anova(alpha.model, beta.model)

summary(alpha.model)
summary(beta.model)
summary(theta.model)
```
But in adolescents' alpha interacts with Reading Comprehension to predict WL Performance
```{r}
adol.alpha.model <- lmer(MP_PC ~ 1 + Alpha*GortCo*age + (1|age), data = adolescents)
adol.beta.model <- lmer(MP_PC ~ 1 + Beta*GortCo*age + (1|age), data = adolescents)
adol.theta.model <- lmer(MP_PC ~ 1 + Theta*GortCo*age + (1|age), data = adolescents)
adol.gamma.model <- lmer(MP_PC ~ 1 + Gamma*GortCo*age + (1|age), data = adolescents)

AIC(adol.alpha.model,adol.beta.model,adol.theta.model,adol.gamma.model)

anova(adol.alpha.model, adol.beta.model)

summary(adol.alpha.model)
summary(adol.beta.model)
summary(adol.theta.model)
summary(adol.gamma.model)
```

## Vocabulary and Word Learning
In younger children, theta interacts with vocabulary to predict WL Performance
```{r}
alpha.model <- lmer(MP_PC ~ 1 + Alpha*PPVT*age + (1|age), data = children)
beta.model <- lmer(MP_PC ~ 1 + Beta*PPVT*age + (1|age), data = children)
theta.model <- lmer(MP_PC ~ 1 + Theta*PPVT*age + (1|age), data = children)

AIC(alpha.model,beta.model,theta.model)

anova(alpha.model, beta.model)

summary(alpha.model)
summary(beta.model)
summary(theta.model)
```

No significant interactions in adolescents
```{r}
adol.alpha.model <- lmer(MP_PC ~ 1 + Alpha*PPVT*age + (1|age), data = adolescents)
adol.beta.model <- lmer(MP_PC ~ 1 + Beta*PPVT*age + (1|age), data = adolescents)
adol.theta.model <- lmer(MP_PC ~ 1 + Theta*PPVT*age + (1|age), data = adolescents)
adol.gamma.model <- lmer(MP_PC ~ 1 + Theta*PPVT*age + (1|age), data = adolescents)

AIC(adol.alpha.model,adol.beta.model,adol.theta.model,adol.gamma.model)

anova(adol.alpha.model, adol.beta.model)

summary(adol.alpha.model)
summary(adol.beta.model)
summary(adol.theta.model)
summary(adol.gamma.model)
```
## Working Memory and Word Learning
```{r}
alpha.model <- lmer(MP_PC ~ 1 + Alpha*DigSpa*age + (1|age), data = children)
beta.model <- lmer(MP_PC ~ 1 + Beta*DigSpa*age + (1|age), data = children)
theta.model <- lmer(MP_PC ~ 1 + Theta*DigSpa*age + (1|age), data = children)

AIC(alpha.model,beta.model,theta.model)

anova(alpha.model, beta.model)

summary(alpha.model)
summary(beta.model)
summary(theta.model)
```
```{r}
adol.alpha.model <- lmer(MP_PC ~ 1 + Alpha*DigSpa*age + (1|age), data = adolescents)
adol.beta.model <- lmer(MP_PC ~ 1 + Beta*DigSpa*age + (1|age), data = adolescents)
adol.theta.model <- lmer(MP_PC ~ 1 + Theta*DigSpa*age + (1|age), data = adolescents)
adol.gamma.model <- lmer(MP_PC ~ 1 + Theta*DigSpa*age + (1|age), data = adolescents)

AIC(adol.alpha.model,adol.beta.model,adol.theta.model,adol.gamma.model)

anova(adol.alpha.model, adol.beta.model)

summary(adol.alpha.model)
summary(adol.beta.model)
summary(adol.theta.model)
summary(adol.gamma.model)
```
### Old analysis below this line:
#########################################################################################################
### Theta LMEM:Compared two models, one with Reading, one without. The model with Reading is a better fit (Chi-square = 7.308523 (df= 1 ), p = 0.006862832), with theta moderately predicting vocabulary (p = 0.08)
```{r}
fm1 <- lmer(PPVT.Raw.Score ~ 1 + Theta_F + Thet_LP + Thet_RP + age + (1|age), data = df_overall)
fm2 <- lmer(PPVT.Raw.Score ~ 1 + Theta_F + Thet_LP + Thet_RP + GortCo + age + (1|age), data = df_overall)

AIC(fm1,fm2)
dev0 <- -2*logLik(fm1) # deviance simpler model
dev1 <- -2*logLik(fm2) # deviance complex model
devdiff <- as.numeric(dev0-dev1) # difference in deviances
dfdiff <- attr(dev1,"df")-attr(dev0,"df") # difference in params (using dfs)
cat('Chi-square =', devdiff, '(df=', dfdiff,'), p =', 
  pchisq(devdiff,dfdiff,lower.tail=FALSE))

summary(fm2)
```
### Plot Theta Effect: Moderate effect of Theta on Vocabulary (note: this graph does NOT account for other effects that are factored out in the LMER)
```{r}
plot(df_overall$PPVT.Raw.Score, df_overall$Theta_F, main="Frontal Theta and Vocabulary",
   xlab="Vocabulary ", ylab="Theta Amplitude ", pch=19)
```
### Plot Theta Effect: There is an interaction between age and frontal theta predicting vocabulary ( p = .04)
```{r}
interact_plot(fm1, pred = Theta_F, modx = age, plot.points = TRUE)
```

### Investigating interaction between Theta and Vocabulary on Word Learning
```{r}
fm1 <- lmer(MAve_A ~ 1 + Theta_F*PPVT.Raw.Score + age + (1|age), data = df_overall)
fm2 <- lmer(MAve_A ~ 1 + Thet_RP*PPVT.Raw.Score + age + (1|age), data = df_overall)
fm3 <- lmer(MAve_A ~ 1 + Thet_LP*PPVT.Raw.Score + age + (1|age), data = df_overall)

AIC(fm1,fm2,fm3)

anova(fm1, fm2)

summary(fm1)
summary(fm2)
summary(fm3)
```
### Investigating interaction between Theta and Vocabulary on Word Learning
```{r}
fm1 <- lmer(MAve_A ~ 1 + Theta_F*age + (1|age), data = df_overall)
fm2 <- lmer(MAve_A ~ 1 + Thet_RP*age + (1|age), data = df_overall)
fm3 <- lmer(MAve_A ~ 1 + Thet_LP*age + (1|age), data = df_overall)

AIC(fm1,fm2,fm3)

anova(fm1, fm2)

summary(fm1)
summary(fm2)
summary(fm3)
```

### Omnibus LMEM: No significant patterns, best fit model is model 1
```{r}
fm1 <- lmer(GortCo ~ 1 + Alp_3m1 + Beta_Glob_2on_S3 + GamGl_3m1 + age + (1|age), data = df_overall)
fm2 <- lmer(GortCo ~ 1 + Alp_3m1 + Beta_Glob_2on_S3 + GamGl_3m1 + PPVT.Raw.Score + age + (1|age), data = df_overall)

AIC(fm1,fm2)
dev0 <- -2*logLik(fm1) # deviance simpler model
dev1 <- -2*logLik(fm2) # deviance complex model
devdiff <- as.numeric(dev0-dev1) # difference in deviances
dfdiff <- attr(dev1,"df")-attr(dev0,"df") # difference in params (using dfs)
cat('Chi-square =', devdiff, '(df=', dfdiff,'), p =', 
  pchisq(devdiff,dfdiff,lower.tail=FALSE))

summary(fm1)
```
### Word Learning LMEMs: Alpha interacts with reading comprehension to predict WL ability (p = 0.0338), there is also a main effect of alpha (p = 0.0141). Beta also predicts WL ability (p = 0.0249). Gamma does not predict WL ability. ** All when controlling for age. 
```{r}
alpha.model <- lmer(MAve_A ~ 1 + Alp_3m1*GortCo + age + (1|age), data = df_overall)
beta.model <- lmer(MAve_A ~ 1 + Beta_Glob_2on_S3*GortCo + age + (1|age), data = df_overall)
gamma.model <- lmer(MAve_A ~ 1 + GamGl_3m1*GortCo + age + (1|age), data = df_overall)

AIC(alpha.model,beta.model,gamma.model)

anova(alpha.model, beta.model)

summary(alpha.model)
summary(beta.model)
summary(gamma.model)
```
```{r}
interact_plot(alpha.model, pred = Alp_3m1, modx = GortCo, plot.points = TRUE)
```
### LMEM of Alpha, Beta or Gamma individually predicting Reading Comprehension. No significant results. 
```{r}
fm1 <- lmer(GortCo ~ 1 + Alp_3m1 + age + (1|age), data = df_overall)
fm2 <- lmer(GortCo ~ 1 + Beta_Glob_2on_S3 + age + (1|age), data = df_overall)
fm3 <- lmer(GortCo ~ 1 + GamGl_3m1 + age + (1|age), data = df_overall)

AIC(fm1,fm2,fm3)

anova(fm1, fm2)

summary(fm1)
summary(fm2)
summary(fm3)
```

### LMEM with Working memory interactions
```{r}
alpha.model <- lmer(MAve_A ~ 1 + Alp_3m1*DigSpa + age + (1|age), data = df_overall)
beta.model <- lmer(MAve_A ~ 1 + Beta_Glob_2on_S3*DigSpa + age + (1|age), data = df_overall)
gamma.model <- lmer(MAve_A ~ 1 + GamGl_3m1*DigSpa + age + (1|age), data = df_overall)

AIC(alpha.model,beta.model,gamma.model)

anova(alpha.model, beta.model)

summary(alpha.model)
summary(beta.model)
summary(gamma.model)
```
### LMEM with Working memory interactions
```{r}
alpha.model <- lmer(MAve_A ~ 1 + Alp_3m1*PPVT.Raw.Score + age + (1|age), data = df_overall)
beta.model <- lmer(MAve_A ~ 1 + Beta_Glob_2on_S3*PPVT.Raw.Score + age + (1|age), data = df_overall)
gamma.model <- lmer(MAve_A ~ 1 + GamGl_3m1*PPVT.Raw.Score + age + (1|age), data = df_overall)

AIC(alpha.model,beta.model,gamma.model)

anova(alpha.model, beta.model)

summary(alpha.model)
summary(beta.model)
summary(gamma.model)
```