---
title: "BL_Maguire_2020"
author: "JM Schneider"
date: "4/30/2020"
output: html_document
---
## Library Import
```{r,include=FALSE,echo=FALSE,warning=FALSE}
#Loading library
library(ez); library(ggplot2); library(multcomp); library(nlme); library(pastecs); library(reshape)
library(Hmisc); library (WRS2); library(lme4); library(lmerTest); library(plyr); library(splitstackshape) 
library(naniar); library(tidyr); library(dplyr); library(memisc); library(psychReport); library(foreign); library(interactions); library(corrplot); library(devtools); library(effects)
```

## Additional Preset and Working Directory
```{r}
#rm(list=ls())

# Max print output.
options(max.print=1e9)
options(dplyr.print_max = 1e10)

setwd("/Users/julieschneider/Julie_Personal/Projects/WLdevdiff/R_Data/")
df_overall=read.csv('BL_Revision_New_Extract.csv')
```

## Make Factors into Numeric Values
```{r}
df_overall$Theta<-as.numeric(df_overall$Theta)
df_overall$Beta<-as.numeric(df_overall$Beta)
df_overall$Alpha<-as.numeric(df_overall$Alpha)
df_overall$Gamma<-as.numeric(df_overall$Gamma)
df_overall$Cont_Age<-as.numeric(df_overall$Cont_Age)
df_overall$PPVT.Raw.Score<-as.numeric(as.character(df_overall$PPVT.Raw.Score))
df_overall$GORT.V....comp<-as.numeric(as.character(df_overall$GORT.V....comp))
df_overall$Digit.Span<-as.numeric(as.character(df_overall$Digit.Span))
df_overall$MP_PC<-as.numeric(as.character(df_overall$MP_PC))
df_overall$PPVT.4.SS<-as.numeric(as.character(df_overall$PPVT.4.SS))
df_overall$MatEd5<-as.factor(as.character(df_overall$MatEd5))

```

## Establish Groups
```{r}
children <- df_overall[which(df_overall$Cont_Age < 132),]
adolescents <- df_overall[which(df_overall$Cont_Age > 156),]
```

## Correlations within each group
```{r}
#adolescents <-rename(adolescents, c("MP_PC"="WL PC"))

myvars <- c("MP_PC","Alpha","Theta","Beta","PPVT.4.SS","GORT.V....comp","Digit.Span")
child_corr_subset <- children[myvars]
adol_corr_subset <- adolescents[myvars]
child_res <-cor(child_corr_subset)
child_res2<-rcorr(as.matrix(child_corr_subset))
#flattenCorrMatrix(child_res2$r, child_res2$P)
#corrplot(child_res2$r, type="upper", order="hclust", 
        # p.mat = child_res2$P, sig.level = 0.05, insig = "blank")
corrplot(child_res2$r, method = "color", type = "upper",addCoef.col="dark grey", tl.col = "black", p.mat = child_res2$P, sig.level = 0.05, insig = "blank", tl.cex = 0.9)
```
```{r}
adol_res <-cor(adol_corr_subset)
adol_res2<-rcorr(as.matrix(adol_corr_subset))
corrplot(adol_res2$r, method = "color", type = "upper",addCoef.col="dark grey", tl.col = "black", p.mat = adol_res2$P, sig.level = 0.05, insig = "blank", tl.cex = 0.9)
```

## Reading and Word Learning
### Children
```{r}

alpha.read.model <- glm(MP_PC ~ 1 + Alpha*GORT.V....comp + Cont_Age, data = children)
beta.read.model <- glm(MP_PC ~ 1 + Beta*GORT.V....comp + Cont_Age, data = children)
theta.read.model <- glm(MP_PC ~ 1 + Theta*GORT.V....comp + Cont_Age, data = children)

AIC(alpha.read.model,beta.read.model,theta.read.model)

anova(alpha.read.model, beta.read.model)

summary(alpha.read.model)
summary(beta.read.model)
summary(theta.read.model)
```
### Adolescents
```{r}
adol.alpha.read.model <- glm(MP_PC ~ 1 + Alpha*GORT.V....comp + Cont_Age, data = adolescents)
adol.beta.read.model <- glm(MP_PC ~ 1 + Beta*GORT.V....comp + Cont_Age , data = adolescents)
adol.theta.read.model <- glm(MP_PC ~ 1 + Theta*GORT.V....comp + Cont_Age, data = adolescents)
adol.gamma.read.model <- glm(MP_PC ~ 1 + Gamma*GORT.V....comp + Cont_Age, data = adolescents)

AIC(adol.alpha.read.model,adol.beta.read.model,adol.theta.read.model,adol.gamma.read.model)

anova(adol.alpha.read.model, adol.beta.read.model)

summary(adol.alpha.read.model)
summary(adol.beta.read.model)
summary(adol.theta.read.model)
summary(adol.gamma.read.model)

sim_slopes(adol.beta.read.model, pred = Beta, modx = GORT.V....comp, johnson_neyman = FALSE)
```

## Vocabulary and Word Learning
### Children
```{r}
alpha.voc.model <- glm(MP_PC ~ 1 + Alpha*PPVT.4.SS + Cont_Age, data = children)
beta.voc.model <- glm(MP_PC ~ 1 + Beta*PPVT.4.SS + Cont_Age , data = children)
theta.voc.model <- glm(MP_PC ~ 1 + Theta*PPVT.4.SS + Cont_Age, data = children)

AIC(alpha.voc.model,beta.voc.model,theta.voc.model)

anova(alpha.voc.model, beta.voc.model)

summary(alpha.voc.model)
summary(beta.voc.model)
summary(theta.voc.model)

sim_slopes(theta.voc.model, pred = Theta, modx = PPVT.4.SS, johnson_neyman = FALSE)
sim_slopes(alpha.voc.model, pred = Alpha, modx = PPVT.4.SS, johnson_neyman = FALSE)

```

### Adolescents
```{r}
adol.voc.alpha.model <- glm(MP_PC ~ 1 + Alpha*PPVT.4.SS + Cont_Age, data = adolescents)
adol.voc.beta.model <- glm(MP_PC ~ 1 + Beta*PPVT.4.SS + Cont_Age, data = adolescents)
adol.voc.theta.model <- glm(MP_PC ~ 1 + Theta*PPVT.4.SS + Cont_Age, data = adolescents)
adol.voc.gamma.model <- glm(MP_PC ~ 1 + Gamma*PPVT.4.SS + Cont_Age, data = adolescents)

AIC(adol.voc.alpha.model,adol.voc.beta.model,adol.voc.theta.model,adol.voc.gamma.model)

anova(adol.voc.alpha.model, adol.voc.beta.model)

summary(adol.voc.alpha.model)
summary(adol.voc.beta.model)
summary(adol.voc.theta.model)
summary(adol.voc.gamma.model)
```

# Plotting
## Reading and Word Learning
### Children have a significant relationship between Reading and WL
```{r}
est<-Effect("GORT.V....comp", partial.residuals=T, beta.read.model)

plot(est, main="Reading and Word Learning Accuracy",
   xlab="GORT Comprehension", ylab="Word Learning Accuracy", pch=19)
```

### Adolescents have a significant relationship between Reading and WL
```{r}
est<-Effect("GORT.V....comp", partial.residuals=T, adol.beta.read.model)

plot(est, main="Reading and Word Learning Accuracy",
   xlab="GORT Comprehension", ylab="Word Learning Accuracy", pch=19)
```

### Adolescents have a significant relationship between Beta and WL
```{r}
est<-Effect("Beta", partial.residuals=T, adol.beta.read.model)

plot(est, main="Beta and Word Learning Accuracy",
   xlab="Beta Amplitude", ylab="Word Learning Accuracy", pch=19)
```

### In Adolescents, there is a moderately significant interaction between beta power and reading, predicting WL 
```{r}
interact_plot(adol.beta.read.model, pred = Beta, modx = GORT.V....comp, plot.points = TRUE)
```

## Vocabulary and Word Learning
### Children have a moderately significant relationship between WL and Alpha
```{r}
est<-Effect("Alpha", partial.residuals=T, alpha.voc.model)

plot(est, main="Alpha and Word Learning Accuracy",
   xlab="Alpha Amplitude", ylab="Word Learning Accuracy", pch=19)
```

### Children have a significant relationship between Vocab and WL
```{r}
est<-Effect("PPVT.4.SS", partial.residuals=T, alpha.voc.model)

plot(est, main="Vocabulary and Word Learning Accuracy",
   xlab="PPVT Standard Score", ylab="Word Learning Accuracy", pch=19)
```

### In Children, there is an interaction between theta power and vocabulary, predicting WL 
```{r}
interact_plot(theta.voc.model, pred = Theta, modx = PPVT.4.SS, plot.points = TRUE)
```

## Adolescents have a significant relationship between Vocabulary and WL
```{r}
est<-Effect("PPVT.4.SS", partial.residuals=T, adol.voc.gamma.model)

plot(est, main="Vocabulary and Word Learning Accuracy",
   xlab="PPVT Standard Score", ylab="Word Learning Accuracy", pch=19)
```